R Packages to Aid in Handling Web Access Logs

### 2015-12-26 paper/paper.Rmd
cleanup, .gitignore improvements

Base R does not have native code to parse URLs, but the \CRANpkg{httr} package \citep{httr} contains a function, `parse_url`, designed to do just thatm built on R's regular expressions. This function is not vectorised, does not make use of compiled code internally, and produces a list rather than data.frame, making looping over a set of URLs to parse each one a time-consuming and awkward experience. This is understandable given the intent behind that function, which is to decompose individual URLs within the context of making HTTP requests, rather than to analyse URLs *en masse*.

\CRANpkg{urltools} contains `url_parse` - which does the same thing as the equivalent `httr` functionality, but in a vectorised way, relying on compiled code, and producing a data.frame. Within the context of parsing and processing access logs, this is far more useful, because it works efficiently over large sets: httr's functionality, which was never designed with vectorisation in mind, does not. Indeed, benchmarking showed that `url_parse` is approximately 570 times faster than httr's equivalent function:

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{parsing_benchmarks}
    \caption{Results of microbenchmark run: url\char`_parse versus httr's equivalent code}
\end{figure}

>>>>

Base R does not have native code to parse URLs, but the \CRANpkg{httr} package \citep{httr} contains a function, \code{parse\_url}, designed to do just that. Built on R's regular expressions, this function is not vectorised, does not make use of compiled code internally, and produces a list rather than data.frame, making looping over a set of URLs to parse each one a time-consuming and awkward experience. This is understandable given the intent behind that function, which is to decompose individual URLs within the context of making HTTP requests, rather than to analyse URLs *en masse*.

\pkg{urltools} contains \code{url_parse} - which does the same thing as the equivalent \pkg{httr} functionality, but in a vectorised way, relying on compiled code, and producing a data.frame. Within the context of parsing and processing access logs, this is far more useful, because it works efficiently over large sets: httr's functionality, which was never designed with vectorisation in mind, does not. Indeed, benchmarking showed that \code{url\_parse} is approximately 570 times faster than httr's equivalent function:

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{parsing_benchmarks}
    \caption{Results of microbenchmark run: \code{url\_parse} versus httr's equivalent code}
\end{figure}

### 2015-12-26 paper/paper.tex
cleanup, .gitignore improvements

Base R does not have native code to parse URLs, but the \CRANpkg{httr}
package \citep{httr} contains a function, \texttt{parse\_url}, designed
to do just thatm built on R's regular expressions. This function is not
vectorised, does not make use of compiled code internally, and produces
a list rather than data.frame, making looping over a set of URLs to
parse each one a time-consuming and awkward experience. This is
understandable given the intent behind that function, which is to
decompose individual URLs within the context of making HTTP requests,
rather than to analyse URLs \emph{en masse}.

\CRANpkg{urltools} contains \texttt{url\_parse} - which does the same
thing as the equivalent \texttt{httr} functionality, but in a vectorised
way, relying on compiled code, and producing a data.frame. Within the
context of parsing and processing access logs, this is far more useful,
because it works efficiently over large sets: httr's functionality,
which was never designed with vectorisation in mind, does not. Indeed,
benchmarking showed that \texttt{url\_parse} is approximately 570 times
faster than httr's equivalent function:

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{parsing_benchmarks}
    \caption{Results of microbenchmark run: url\char`_parse versus httr's equivalent code}
\end{figure}

>>>>

Base R does not have native code to parse URLs, but the \CRANpkg{httr}
package \citep{httr} contains a function, \code{parse\_url}, designed to
do just that. Built on R's regular expressions, this function is not
vectorised, does not make use of compiled code internally, and produces
a list rather than data.frame, making looping over a set of URLs to
parse each one a time-consuming and awkward experience. This is
understandable given the intent behind that function, which is to
decompose individual URLs within the context of making HTTP requests,
rather than to analyse URLs \emph{en masse}.

\pkg{urltools} contains \code{url_parse} - which does the same thing as
the equivalent \pkg{httr} functionality, but in a vectorised way,
relying on compiled code, and producing a data.frame. Within the context
of parsing and processing access logs, this is far more useful, because
it works efficiently over large sets: httr's functionality, which was
never designed with vectorisation in mind, does not. Indeed,
benchmarking showed that \code{url\_parse} is approximately 570 times
faster than httr's equivalent function:

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{parsing_benchmarks}
    \caption{Results of microbenchmark run: \code{url\_parse} versus httr's equivalent code}
\end{figure}
